---
title: "Survival-related analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{surv}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}

if(!require(biodata)) {
  devtools::install_github("Jinjin89/biodata")
  library(biodata)
}

table(tcga_clin_xena$stage)
table(tcga_clin_xena$Age_group)
summary(tcga_clin_xena$age)


```

# perform survival analysis


what is has?
  
  1. survival K-M
  
  2. uni-cox 
  
  3. multi-cox
  
  4. survival roc
  
  4. nomogram

## Dived variables into high and low group

```{r cutoff}

input_variables =  c("age")
output_variables_names = c("age_group")

tcga_clin_xena %>% 
  fun_surv_cutoff(
    input_variables =input_variables,
    output_variables_names = output_variables_names,
    input_pct= seq(0.25,0.75,0.01)) %>% 
  count(age_group)

# is isnull pct, do nothing
tcga_clin_xena %>% 
  fun_surv_cutoff(
    input_variables =input_variables,
    output_variables_names = output_variables_names,
    input_pct= NULL)

```

## unicox analysis


```{r unicox}

# if data is character, calculate themee logrank

tcga_clin_xena %>% 
    fun_surv_cutoff(
    input_variables =input_variables,
    output_variables_names = output_variables_names,
    input_pct= 0.5) %>% 
  fun_surv_unicox(
    input_variables = output_variables_names)

# if data is numeric, do not calculate km 
tcga_clin_xena %>% 
  fun_surv_unicox(
    input_variables = input_variables)

tcga_clin_xena %>% 
  fun_surv_unicox(
    input_variables = input_variables,
    input_pct = 0.5)



# 3) data with more than two groups
tcga_clin_xena %>% 
  fun_surv_unicox(
    input_variables = "stage")


# 4) unicox analysis
tcga_clin_xena %>% 
  fun_surv_unicox(
    input_variables = c(input_variables,"stage")
  )

```


## multicox analysis

```{r multicox}
tcga_clin_xena %>% 
  fun_surv_multicox(
    input_variables = c(input_variables,"stage")
  )

```


## kmplot

you only need input variables, and data.frame with time,status,<variables>

```{r kmplot}

tcga_clin_xena %>% 
  head(100) %>% 
  # mutate(stage = factor(stage,levels = c("STAGE III","STAGE II","STAGE IV"))) %>% 
  fun_plot_surv_km(input_variables = "stage")


# cutoff age
tcga_clin_xena %>% 
  head(100) %>% 
  fun_plot_surv_km(
    input_variables = "age",
    input_pct = 0.5
  )


```



## timeROC
`fun_time_roc_list` with a *_list* suffix, means the output of `fun_time_roc_list` is a list object.

if `merge_roc_auc` is `TRUE`(default), The roc/auc of each `input_variables` would be merged into one data.frame respectively, So the results would be a list contains two data.frame, namely, roc and auc. roc contains the roc curves for all input_variables, so to auc data.frame

if `merge_roc_auc` is `FALSE`, The output would be also a list, which contains the roc/auc output for each `input_variables`. So length of the returned list is the same as the length of `input_variables`, each element in the returned list contains the roc and auc for each `input_variables`

```{r surv_roc_step}

# merge the output into two dataframe
res = 
  tcga_clin_xena %>% 
  head() %>% 
  fun_surv_roc(
    input_variables = input_variables,
    merge_roc_auc=T 
  )

res$roc %>% head
res$auc %>% head

# Not merge 
res = 
  tcga_clin_xena %>% 
  head() %>% 
  fun_surv_roc(
    input_variables = input_variables,
    merge_roc_auc=F
  )
names(res)

```

## plot timeROC

```{r plot_time_roc}


```


## survival concordance

